%-------------------------
% Resume in LaTeX — Rafael Pinto
% Based on the "Resume in LateX" template (Sourabh Bajaj, MIT License)
% Structure optimized for ATS parsing and fast recruiter skim (see Template.tex
% for notes on why this section order/formatting was chosen).
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemSimple}[1]{
  \item\small{#1 \vspace{-2pt}}
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Rafael Pinto} & Email: \href{mailto:rafael-pinto@outlook.com.br}{rafael-pinto@outlook.com.br}\\
  \href{https://www.linkedin.com/in/rafaelpinto1/}{linkedin.com/in/rafaelpinto1} & Phone: \href{tel:+5521985900023}{+55 21 98590-0023} \\
  \href{https://github.com/rafaelpinto}{github.com/rafaelpinto} & Lattes CV: \href{http://lattes.cnpq.br/2078391939625415}{lattes.cnpq.br/2078391939625415} \\
\end{tabular*}

\begin{center}
  \small\textit{Versão em português disponível para download: }\href{https://raw.githubusercontent.com/rafaelpinto1/portfolio/main/Curriculo_latEX/Rafael_Pinto_CV_PT.pdf}{Rafael\_Pinto\_CV\_PT.pdf}
\end{center}


%-----------SUMMARY-----------------
\section{Summary}
  \resumeSubHeadingListStart
    \resumeItemSimple{Data \& Artificial Intelligence professional with 3+ years of experience delivering Generative AI (LLMs, RAG, AI Agents) and Data Engineering solutions on Microsoft Fabric, Python, and SQL across multiple concurrent clients. M.Sc. candidate in Computer Science (research line: TinyML) at CEFET/RJ, applying that research as a technical edge to optimize data and AI systems in production.}
  \resumeSubHeadingListEnd


%-----------CORE COMPETENCIES-----------------
\section{Core Competencies}
  \resumeSubHeadingListStart
    \resumeItemSimple{Machine Learning \& Generative AI (LLMs, RAG, AI Agents) $\vert$ Microsoft Fabric \& Power BI (Advanced DAX) $\vert$ Data Engineering (ETL/ELT) $\vert$ Python \& Advanced SQL $\vert$ Cloud (Microsoft Azure) $\vert$ Process Automation (n8n) $\vert$ TinyML}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Multipla Tecnologia da Informação Ltda}{Rio de Janeiro, Brazil}
      {Data Analyst}{February 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Generative AI}
          {Architected and delivered Generative AI solutions using LLMs, RAG, and AI Agents to automate analysis and querying of corporate data.}
        \resumeItem{Development}
          {Built Python applications and automations, with version control via Git/GitHub and CI/CD through Azure DevOps.}
        \resumeItem{Data Integration}
          {Implemented critical data pipelines and integrations with Microsoft Fabric, REST APIs, and Microsoft Graph API.}
        \resumeItem{Microsoft Fabric}
          {Administered Capacities, Lakehouses, Data Pipelines, and Semantic Models in Microsoft Fabric, ensuring performance and scalability.}
        \resumeItem{Governance}
          {Built monitoring and governance solutions for Fabric environment consumption analysis, supporting capacity-planning decisions.}
        \resumeItem{Data Sources}
          {Integrated corporate data from SQL Server, Oracle, and other sources into a unified analytics environment.}
        \resumeItem{Observability}
          {Implemented data-environment observability with Zabbix and Grafana, reducing incident diagnosis time.}
        \resumeItem{Project Delivery}
          {Delivered Data, AI, and Analytics projects for multiple concurrent clients, independently managing priorities and deadlines.}
      \resumeItemListEnd

    \resumeSubheading
      {LMG Bonfim Serviço e Apoio Administrativo Ltda}{Rio de Janeiro, Brazil}
      {IT Support Technician}{December 2017 -- January 2023}
      \resumeItemListStart
        \resumeItem{Reporting}
          {Prepared technical reports and tracked operational indicators to support management decisions.}
        \resumeItem{Support}
          {Provided support for and integrated POS systems and remote infrastructure in a corporate environment.}
        \resumeItem{Ticketing}
          {Analyzed and resolved technical support tickets, prioritizing critical incidents.}
      \resumeItemListEnd

    \resumeSubheading
      {Inbrands S.A.}{Rio de Janeiro, Brazil}
      {Administrative Assistant}{August 2015 -- December 2017}
      \resumeItemListStart
        \resumeItem{Inventory}
          {Controlled inventory and issued reports in ERP system.}
        \resumeItem{Support}
          {Supported asset maintenance and provided basic IT support.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Interactive Sales Dashboard -- Power BI, SQL, DAX}
      {Designed an executive dashboard with dynamic customer segmentation, trend analysis, and demand forecasting, enabling real-time decisions without IT dependency.}
    \resumeSubItem{Customer Churn Prediction Model -- Python, Scikit-learn, Pandas}
      {Trained a classifier to identify customer churn risk before it happens, with feature importance analysis and business metrics.}
    \resumeSubItem{Automated ETL Pipeline -- Python, SQLite}
      {Built a log ingestion, transformation, and load solution with end-to-end traceability, failure alerts, and structured logging, reducing manual intervention in the data pipeline.}
  \resumeSubHeadingListEnd

  \textit{\small All projects use synthetic, anonymized data in compliance with Brazil's LGPD (data protection law).}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CEFET/RJ -- Centro Federal de Educação Tecnológica Celso Suckow da Fonseca}{Rio de Janeiro, Brazil}
      {M.Sc. in Computer Science -- Research line: TinyML (Tiny Machine Learning)}{In progress -- expected completion 2028}
    \resumeSubheading
      {UNISUAM -- Centro Universitário Augusto Motta}{Rio de Janeiro, Brazil}
      {Postgraduate Degree in Data Science and Artificial Intelligence}{Completed -- December 2025}
    \resumeSubheading
      {UNISUAM -- Centro Universitário Augusto Motta}{Rio de Janeiro, Brazil}
      {B.Sc. in Systems Analysis and Development}{Completed -- December 2024}
  \resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubItem{Microsoft Certified: Azure Fundamentals (AZ-900)}
      {Microsoft Corporation -- 2026}
    \resumeSubItem{Oracle AI Foundations Associate (1Z0-1195)}
      {Oracle -- 2025}
  \resumeSubHeadingListEnd


%--------SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{AI \& AI Engineering}{: LLMs, Generative AI, RAG, AI Agents, Prompt Engineering, TinyML, Computer Vision, OCR}
    }
    \item{
      \textbf{Data \& Analytics}{: Microsoft Fabric, Power BI, Advanced DAX, Power Query M, Direct Lake, Lakehouse, ETL/ELT, Advanced SQL, Python}
    }
    \item{
      \textbf{Development \& Integration}{: REST APIs, Microsoft Graph API, Git/GitHub, Azure DevOps, Azure Functions, Selenium, Azure (AZ-900)}
    }
    \item{
      \textbf{Automation \& Monitoring}{: n8n, Webhooks, Zabbix, Grafana}
    }
    \item{
      \textbf{Languages}{: Portuguese (native), English (B1)}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
